---
title: "Exploratory Data Analysis Starter"
author: "YU Class"
date: "7/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Use this script!

Coders use templates and code snippets all the time to start their analysis or find solutions to common problems. This is intended to be a starting point for a number of projects you will work on going forward.

Things we will commonly want to do in an RMarkdown:

* Import data (from a .csv, from an API, etc.)
* Tidy data (ensure it is structured in a consistent tabular format)
* Exploratory cycle - visualize, transform
* Narrative, share, export - you're done!

### Import data

This step usually requires using the `readr` library, which is happy grabbing data from a variety of sources.

We want to bring in a .csv from a location online AND store it in a variable we can use

```{r message=FALSE}
covid_concern <- read_csv('https://raw.githubusercontent.com/fivethirtyeight/covid-19-polls/master/covid_concern_polls.csv')

head(covid_concern)
```


We'd like to compare the distributions of "very", "somewhat", "not-very", and "not-at-all" responses across all polls.

```{r message=FALSE}
covid_concern_long <- covid_concern %>%
  pivot_longer(c('very', 'somewhat', 'not_very', 'not_at_all'), names_to = "response", values_to = "response_percentage") %>%
  select('start_date', 'pollster', 'subject', 'response', 'response_percentage')

covid_concern_long %>%
  filter(subject=="concern-infected") %>%
  ggplot(mapping = aes(y = response_percentage, fill = response)) +
  geom_boxplot()

```


