---
title: "Exploratory Data Analysis Starter"
author: "YU Class"
date: "7/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Use this script!

Coders use templates and code snippets all the time to start their analysis or find solutions to common problems. This is intended to be a starting point for a number of projects you will work on going forward.

Things we will commonly want to do in an RMarkdown:

* Import data (from a .csv, from an API, etc.)
* Tidy data (ensure it is structured in a consistent tabular format)
* Exploratory cycle - visualize, transform
* Narrative, share, export - you're done!

### Import data

This step usually requires using the `readr` library, which is happy grabbing data from a variety of sources.

We want to bring in a .csv from a location online AND store it in a variable we can use

```{r}
covid_polling_data <- read_csv('https://raw.githubusercontent.com/fivethirtyeight/covid-19-polls/master/covid_approval_polls.csv')

head(covid_polling_data)
```



When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
